### 2018-11-29 2018_nips_vigil_poster/main.tex
Finalize Equations & Datasets section.

\documentclass[final,paperwidth=36in,paperheight=48in,portrait,fontscale=0.36]{baposter}
% NIPS Workshops format

@@

\usepackage{graphicx} % Required for including images
\usepackage{booktabs} % for professional tables
\usepackage{floatrow}
\usepackage{amsmath} % For typesetting math
\usepackage[font=small,labelfont=bf, justification=centering]{caption} % Required for specifying captions to tables and figures

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\headerbox{Summary}{name=summary,column=0,row=0}{
\begin{itemize}
	\compresslist
	\item[$\bullet$] We introduce a simplified variant of the MAC model (\textit{Hudson and Manning, ICLR 2018}), which achieves comparable accuracy while training faster.
	\item[$\bullet$] We evaluate both models on CLEVR \& CoGenT, and show that, transfer learning with fine-tuning results in a 15 point increase in accuracy, matching the state of the art.
	\item[$\bullet$] We also demonstrate that improper fine-tuning can reduce a model's accuracy.

@@

\makebox[\textwidth]{MAC  \\[5cm] S-MAC}\\
\noindent\textbf{Control unit:} The question $q$ is first made \emph{position-aware} in each reasoning step using an $i$-dependent projection: $q_i = U_i^{[d \times 2d]} q + b_i^{[d]}$.

\begin{multicols}{2}
	\noindent
	\begin{align*}
	&cq_i = W_{cq}^{[d \times 2d]} [c_{i-1}, q_i] + b_{cq}^{[d]}  \tag{c1} \\
	&ca_{is} = W_{ca}^{[1 \times d]} (cq_i \odot \cw_s) + b_{ca}^{[1]}
	\tag{c2.1}\\
	&cv_{is} = \textrm{softmax}(ca_{is}) \tag{c2.2}\\
	&\cc_i = \sum_s cv_{is} \, \cw_s  \tag{c2.3}
	\end{align*}
	\columnbreak
	{
		\begin{align*}
		&cq_i = W_{cq}^{[d \times d]} c_{i-1} + q_i  \tag{c1} \\
		&ca_{is} = W_{ca}^{[1 \times d]} (cq_i \odot \cw_s)  \tag{c2.1}\\
		&cv_{is} = \textrm{softmax}(ca_{is}) \tag{c2.2}\\
		&\cc_i = \sum_s cv_{is} \, \cw_s  \tag{c2.3}
		\end{align*}}
\end{multicols}

@@

\noindent\textbf{Read and write units:}
\begin{multicols}{2}
	\noindent
	\begin{align*}
	&I_{ihw} = (W_{m}^{[d \times d]} \mem_{i-1} + b_{m}^{[d]}) \\
	& \qquad \quad \odot (W_{k}^{[d \times d]} \kb_{hw} + b_{k}^{[d]}) \tag{r1} \\
	&I'_{ihw} =  W_{I'}^{[d \times 2d]} [I_{ihw},\kb_{hw}]  + b_{I'}^{[d]}  \tag{r2} \\
	&ra_{ihw} = W_{ra}^{[1 \times d]} (\cc_i \odot I'_{ihw}) + b_{ra}^{[1]} \tag{r3.1}\\
	&rv_{ihw} = \textrm{softmax}(ra_{ihw}) \tag{r3.2}\\
	&\rr_i = \sum_s rv_{ihw} \, \kb_{hw}  \tag{r3.3}\\
	&\mem_i = W_{rm}^{[d \times d]} [\rr_i, \mem_{i-1}]  + b_{rm}^{[d]} \tag{w1}	
	\end{align*}
	\columnbreak
	{
		\begin{align*}
		&I_{ihw} = m _{i-1} \odot k _{hw} \tag{r1} \\ 
		&I'_{ihw} = W_{I'}^{[d \times d]} I_{ihw} + b_{I'}^{[d]} + \kb_{hw} \tag{r2} \\
		&ra_{ihw} = W_{ra}^{[1 \times d]} (\cc_i \odot I'_{ihw})  \tag{r3.1}\\
		&rv_{ihw} = \textrm{softmax}(ra_{ihw}) \tag{r3.2}\\
		&\rr_i = \sum_s rv_{ihw} \, \kb_{hw}  \tag{r3.3}\\
		&\mem_i = W_{rm}^{[d \times 2d]} \rr_i + b_{rm}^{[d]} \tag{w1}
		\end{align*}}
\end{multicols}

\begin{table}[H]
	\centering
	\caption{Comparing the number of position-independent parameters between MAC \& S-MAC cells.}
	\begin{tabular}{llll}
		\toprule
		Model        & Read Unit               & Write Unit &  Control Unit         \\
		\midrule
		MAC   &  787,969 &  524,800        &    525,313    \\
		%\midrule
		simplified MAC & 263,168  & 262,656       &    263,168 \\
		\midrule
		Reduction by [\%]  & 67\%  &   50\%       &      50\%  \\
		\bottomrule
	\end{tabular}
	\label{tab:mac_cell_parameters}
\end{table}

@@

\headerbox{Datasets - CLEVR and CoGenT}{name=dataset, column=1}{
The CLEVR task:
		\begin{figure}[H]
		\centering
		\includegraphics[width=0.31\textwidth]{../img/teaser.jpg}
	    \end{figure}

    \begin{description}
    	\centering
    	\item[$\cdot$] \textit{How many objects are either small cylinders or red things?}

   \begin{description}
   	\item[$\bullet$]Along with CLEVR, the authors~\cite{johnson2017clevr} introduced  CLEVR-CoGenT 
   	\item[$\bullet$] The goal is to evaluate how well the models can generalize, learn relations and compositional concepts.
   	\item[$\bullet$] This dataset is generated in the same way as CLEVR, with two conditions, A and B. as shown in Table 2.

	\begin{table}[H]
		\centering
		\begin{tabular}{llll}
			\toprule
			Dataset        & Cubes              & Cylinders &  Spheres         \\
			\midrule
			CLEVR   &  any color &  any color        &    any color    \\
			CLEVR CoGenT A & gray / blue / brown / yellow  & red / green / purple / cyan       &    any color  \\
			CLEVR CoGenT B  & red / green / purple / cyan &   gray / blue / brown / yellow       &      any color  \\
			\bottomrule
		\end{tabular}
		\caption{Colors/shapes combinations present in CLEVR, CoGenT-A and CoGenT-B datasets.}
		\label{tab:cogent_conditions}
	\end{table}

@@

\headerbox{Transfer Learning - Experiments}{name=transfer, column=1, below=dataset}{

CLEVR \& CoGenT accuracies for the MAC \& S-MAC models:
	\begin{table}[H]
	\centering
	\scalebox{1}{
	\begin{tabular}{lllllllll}
		\toprule
		\multirow{2}{*}{Model} & \multicolumn{3}{c}{Training} &  \multicolumn{2}{c}{Fine-tuning} & \multicolumn{2}{c}{Test} & \multirow{2}{*}{Row} \\
		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
		& Dataset                & Time [h:m] & Acc [\%]          & Dataset & Acc [\%]  & Dataset & Acc [\%] & \\
		\midrule
		MAC & CLEVR  & 30:52  & 96.70 & --   & --  & CLEVR    & 96.17         & (a) \\
		\cmidrule{1-8}
		\cmidrule{1-8}

		\multirow{13}{*}{S-MAC} & CLEVR  & 28:30  & 95.82 & --   & --  & CLEVR    & 95.29         & (b)  \\
		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8}

		& CoGenT-A  & 28:33   & 96.09 &  --  &  --  & CoGenT-A & 95.91        & (c)  \\
		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8}

		& \multirow{2}{*}{CLEVR}  & \multirow{2}{*}{28:30}  & \multirow{2}{*}{95.82} & \multirow{2}{*}{--}   & \multirow{2}{*}{--}  &   CoGenT-A    &  95.47  & (d) \\
		\cmidrule{7-8} 
		&                        &   &              &     &                               & CoGenT-B   &  95.58  & (e)\\

		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
		& \multirow{4}{*}{CoGenT-A}   & \multirow{4}{*}{28:33}   & \multirow{4}{*}{96.09}  &  \multirow{1}{*}{--}  &  \multirow{1}{*}{--}   & CogenT-B & 78.71        & (f)  \\
		\cmidrule{5-6} \cmidrule{7-8} 
		&                             &                                         &    &   \multirow{2}{*}{CoGenT-B}         &       \multirow{2}{*}{96.85}          & CoGenT-A &  91.24        & (g) \\
		\cmidrule{7-8} 
		&                             &                                         &       &         &                & CoGenT-B &    94.55     & (h)  \\

		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
		& \multirow{2}{*}{CLEVR}  & \multirow{2}{*}{28:30}  & \multirow{2}{*}{95.82} &   \multirow{2}{*}{CoGenT-B}         &       \multirow{2}{*}{97.67}          & CoGenT-A &  92.11       & (i) \\
		\cmidrule{7-8} 
		&                             &                                         &       &         &                & CoGenT-B &    92.95    & (j)  \\

@@

\headerbox{MAC drawbacks on CLEVR}{name=baseline, column=1, below=transfer}{

>>>>

\documentclass[paperwidth=36in,paperheight=48in,portrait,fontscale=0.36]{baposter}
% NIPS Workshops format

@@

\usepackage{graphicx} % Required for including images
\usepackage{booktabs} % for professional tables
\usepackage{floatrow}
\usepackage{amsmath} % For typesetting math
\usepackage[labelfont=bf, justification=centering]{caption} % Required for specifying captions to tables and figures

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\headerbox{Summary}{name=summary,column=0,row=0}{
\begin{itemize}
	\compresslist
	\item[$\bullet$] We introduce a \emph{\textbf{simplified}} variant of the MAC model (\textit{Hudson and Manning, ICLR 2018}), which achieves comparable accuracy while training \emph{\textbf{faster}}.
	\item[$\bullet$] We evaluate both models on CLEVR \& CoGenT, and show that, \emph{\textbf{transfer learning with fine-tuning}} results in a 15 point increase in accuracy, matching the state of the art.
	\item[$\bullet$] We also demonstrate that \emph{\textbf{improper}} fine-tuning can reduce a model's accuracy.

@@

\makebox[\textwidth]{\textbf{MAC \\[5cm] S-MAC}}\\
\vspace{-5pt}
\hrule
\vspace{10pt}
\noindent\textbf{Control unit:} The question $q$ is first made \emph{position-aware} in each reasoning step using an $i$-dependent projection: $q_i = U_i^{[d \times 2d]} q + b_i^{[d]}$.

\begin{multicols}{2}
	\noindent
	\begin{align*}
		&cq_i = W_{cq}^{[d \times 2d]} [c_{i-1}, q_i] + b_{cq}^{[d]}  \tag{c1} \\
		&ca_{is} = W_{ca}^{[1 \times d]} (cq_i \odot \cw_s) + b_{ca}^{[1]}
		\tag{c2.1}\\
		&cv_{is} = \textrm{softmax}(ca_{is}) \tag{c2.2}\\
		&\cc_i = \sum_s cv_{is} \, \cw_s  \tag{c2.3}
	\end{align*}
	\columnbreak
	{\begin{align*}
		&cq_i = W_{cq}^{[d \times d]} c_{i-1} + q_i  \tag{c1} \\
		&ca_{is} = W_{ca}^{[1 \times d]} (cq_i \odot \cw_s)  \tag{c2.1}\\
		&cv_{is} = \textrm{softmax}(ca_{is}) \tag{c2.2}\\
		&\cc_i = \sum_s cv_{is} \, \cw_s  \tag{c2.3}
	\end{align*}}
\end{multicols}

@@

\noindent\textbf{Read and write units:}
\begin{multicols}{2}
	\noindent
	\begin{align*}
		&I_{ihw} = (W_{m}^{[d \times d]} \mem_{i-1} + b_{m}^{[d]}) \\
		& \qquad \quad \odot (W_{k}^{[d \times d]} \kb_{hw} + b_{k}^{[d]}) \tag{r1} \\
		&I'_{ihw} =  W_{I'}^{[d \times 2d]} [I_{ihw},\kb_{hw}]  + b_{I'}^{[d]}  \tag{r2} \\
		&ra_{ihw} = W_{ra}^{[1 \times d]} (\cc_i \odot I'_{ihw}) + b_{ra}^{[1]} \tag{r3.1}\\
		&rv_{ihw} = \textrm{softmax}(ra_{ihw}) \tag{r3.2}\\
		&\rr_i = \sum_s rv_{ihw} \, \kb_{hw}  \tag{r3.3}\\
		&\mem_i = W_{rm}^{[d \times d]} [\rr_i, \mem_{i-1}]  + b_{rm}^{[d]} \tag{w1}
	\end{align*}
	\columnbreak
	{\begin{align*}
		&I_{ihw} = m _{i-1} \odot k _{hw} \tag{r1} \\ 
		&I'_{ihw} = W_{I'}^{[d \times d]} I_{ihw} + b_{I'}^{[d]} + \kb_{hw} \tag{r2} \\
		&ra_{ihw} = W_{ra}^{[1 \times d]} (\cc_i \odot I'_{ihw})  \tag{r3.1}\\
		&rv_{ihw} = \textrm{softmax}(ra_{ihw}) \tag{r3.2}\\
		&\rr_i = \sum_s rv_{ihw} \, \kb_{hw}  \tag{r3.3}\\
		&\mem_i = W_{rm}^{[d \times 2d]} \rr_i + b_{rm}^{[d]} \tag{w1}
	\end{align*}}
\end{multicols}

\vspace{-15pt}
\begin{table}[H]
	\centering
	\caption{Comparing the number of position-independent parameters between MAC \& S-MAC cells.}
	\begin{tabular}{llll}
		\toprule
		Model        & Read Unit               & Write Unit &  Control Unit         \\
		\midrule
		MAC   &  787,969 &  524,800        &    525,313    \\
		S-MAC & 263,168  & 262,656       &    263,168 \\
		\midrule
		Reduction by [\%]  & 67\%  &   50\%       &      50\%  \\
		\bottomrule
	\end{tabular}
	\label{tab:mac_cell_parameters}
\end{table}

@@

\headerbox{The CLEVR \& CoGenT datasets}{name=datasets, column=1}{
	\vspace{-10pt}
	\begin{figure}[H]
		\includegraphics[width=0.4\textwidth]{../img/teaser.jpg}
		\caption{\textit{How many objects are either small cylinders or red things?}}
		\label{fig:clevr_task}
	\end{figure}
	\vspace{-10pt}
	\begin{itemize}
	  	\compresslist
	  	\item[$\bullet$] The authors~\cite{johnson2017clevr} also introduced CLEVR-CoGenT, to evaluate how well a model can learn relations and compositional concepts.
	  	\item[$\bullet$] Similar to CLEVR, but with two conditions, as follows:
	\end{itemize}
	\vspace{-10pt}
	\begin{table}[H]
		\centering
		\begin{tabular}{llll}
			\toprule
			Dataset        & Cubes              & Cylinders &  Spheres         \\
			\midrule
			CLEVR   &  any color &  any color        &    any color    \\
			CLEVR CoGenT-A & gray / blue / brown / yellow  & red / green / purple / cyan       &    any color  \\
			CLEVR CoGenT-B  & red / green / purple / cyan &   gray / blue / brown / yellow       &      any color  \\
			\bottomrule
		\end{tabular}
		\caption{Colors/shapes combinations present in CLEVR, CoGenT-A and CoGenT-B datasets.}
		\label{tab:cogent_conditions}
	\end{table}

@@

\headerbox{Experiments \& Results}{name=experiments, column=1, below=datasets}{

CLEVR \& CoGenT accuracies for the MAC \& S-MAC models:
	\begin{table}[H]
	\centering
	\scalebox{1}{
	\begin{tabular}{cccccccc}
		\toprule
		\multirow{2}{*}{Model} & \multicolumn{3}{c}{Training} &  \multicolumn{2}{c}{Fine-tuning} & \multicolumn{2}{c}{Test} \\
		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
		& Dataset                & Time [h:m] & Acc [\%]          & Dataset & Acc [\%]  & Dataset & Acc [\%] \\
		\midrule
		MAC & CLEVR  & 30:52  & 96.70 & --   & --  & CLEVR    & 96.17 \\
		\cmidrule{1-8}
		\cmidrule{1-8}

		\multirow{13}{*}{S-MAC} & CLEVR  & 28:30  & 95.82 & --   & --  & CLEVR    & 95.29 \\
		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8}

		& CoGenT-A  & 28:33   & 96.09 &  --  &  --  & CoGenT-A & 95.91 \\
		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8}

		& \multirow{2}{*}{CLEVR}  & \multirow{2}{*}{28:30}  & \multirow{2}{*}{95.82} & \multirow{2}{*}{--}   & \multirow{2}{*}{--}  &   CoGenT-A    &  95.47 \\
		\cmidrule{7-8} 
		&                        &   &              &     &                               & CoGenT-B   &  95.58  \\

		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
		& \multirow{4}{*}{CoGenT-A}   & \multirow{4}{*}{28:33}   & \multirow{4}{*}{96.09}  &  \multirow{1}{*}{--}  &  \multirow{1}{*}{--}   & CogenT-B & 78.71 \\
		\cmidrule{5-6} \cmidrule{7-8} 
		&                             &                                         &    &   \multirow{2}{*}{CoGenT-B}         &       \multirow{2}{*}{96.85}          & CoGenT-A &  91.24 \\
		\cmidrule{7-8} 
		&                             &                                         &       &         &                & CoGenT-B &    94.55 \\

		\cmidrule{2-4} \cmidrule{5-6} \cmidrule{7-8} 
		& \multirow{2}{*}{CLEVR}  & \multirow{2}{*}{28:30}  & \multirow{2}{*}{95.82} &   \multirow{2}{*}{CoGenT-B}         &       \multirow{2}{*}{97.67}          & CoGenT-A &  92.11 \\
		\cmidrule{7-8} 
		&                             &                                         &       &         &                & CoGenT-B &    92.95 \\

@@

\headerbox{MAC drawbacks on CLEVR}{name=baseline, column=1, below=experiments}{
